\sysfull

### 2017-11-05 paper/intro.tex
multipages results for 128 and 64 bytes page sizes
text for virtualization

\textbf{Static Task-based Model and its Inefficiency:} The latest two {\em task-based} programming and execution models~\cite{alpaca,chain} advocate for static decomposition of a program (by a programmer) into a collection of tasks. Tasks can include arbitrary computation and, upon completion, are guaranteed to have executed {\em atomically}, despite arbitrarily-timed power failures. The programmer explicitly expresses task-to-task control flow, which may be conditionally input-dependent. A key challenge is that the length of a software task's execution is \emph{limited by the fixed total amount of energy} that a device can buffer in hardware. A task's code is static, but the duration of its execution may be input-dependent and is difficult to predict. To illustrate this, we refer to Figure~\ref{fig:1} showing the execution time of two applications (the same application X, but divided into X and Y tasks as in~\cite{chain}) running on RFID antenna-powered Computational RFID~\cite{wisp,rf_powered_computing_gollakota_2014} at two device-to-antenna distances (near---stable energy supply/far---high energy intermittency). At short distance: execution will takes too long caused by runtime cost of marshalling excessively small tasks. At far distance: program \emph{might never execute} if task execution consumes more energy than the system can buffer. This calls for at-runtime task division of any transiently-powered application.

\textbf{Data Inconsistency of Virtual Task:} Task-based model which allows for dynamic task division must implement \emph{task virtualization mechanism}: merging of atomic, data-consistent tasks into a single (larger) task. This however induces a problem of \emph{virtual task write-after-read (WAR) dependency violation}. Consider the following example of Task 1: {\tt{\{y=x+1;\}}}, Task 2: {\tt{\{z=y+1;\}}}, and Task 3 {\tt{\{x=z+1;\}}} being executed consecutively. All tasks have no WAR dependency and are consistent. Now, suppose three tasks have been virtualized into one, namely Task 4: {\tt{\{y=x+1; z=y+1; x=z+1;\}}} which has inherent WAR dependency (variable {\tt{x}}).

>>>>

\textbf{\replace{Static Task-based Model and its Inefficiency:}{The Inefficiency of Static Task-based Models}} The latest two {\em task-based} programming and execution models~\cite{alpaca,chain} advocate for static decomposition of a program (by a programmer) into a collection of tasks. Tasks can include arbitrary computation and, upon completion, are guaranteed to have executed {\em atomically}, despite arbitrarily-timed power failures. The programmer explicitly expresses task-to-task control flow, which may be conditionally input-dependent. A key challenge is that the length of a software task's execution is \emph{limited by the fixed total amount of energy} that a device can buffer in hardware. A task's code is static, but the duration of its execution may be input-dependent and is difficult to predict. To illustrate this, we refer to Figure~\ref{fig:1} showing the execution time of two applications (the same application X, but divided into X and Y tasks as in~\cite{chain}) running on RFID antenna-powered Computational RFID~\cite{wisp,rf_powered_computing_gollakota_2014} at two device-to-antenna distances (near---stable energy supply/far---high energy intermittency). At short distance: execution will takes too long caused by runtime cost of marshalling excessively small tasks. At far distance: program \emph{might never execute} if task execution consumes more energy than the system can buffer. This calls for at-runtime \add{adaptive} task division of any transiently-powered application\add{---namely \emph{task virtualization}}.

\begin{figure}
	\includegraphics[width=0.6\columnwidth]{presentation/images/alpaca-war.pdf}
	\caption{\label{fig:virtualization}\color{blue} Adaptive task division at run-time might lead to WAR dependencies that do not exist with static task division.}
\end{figure}

\textbf{\replace{Data Inconsistency of Virtual Task:}{The Challange Behind Task Virtualization}} Task-based model which allows for dynamic task division must implement \emph{task virtualization mechanism}: merging of atomic, data-consistent tasks into a single (larger) task. This however \replace{induces a problem of \emph{virtual task write-after-read (WAR) dependency violation}}{might introduce new \emph{write-after-read (WAR)} dependencies at \emph{run-time} that can break the atomicity of the \emph{virtual task}. Consider the example depicted in Fig.~\ref{fig:virtualization}: Tasks 1--3 being executed consecutively.} \remove{Consider the following example of Task 1: {\tt{\{y=x+1;\}}}, Task 2: {\tt{\{z=y+1;\}}}, and Task 3 {\tt{\{x=z+1;\}}} being executed consecutively.} All tasks \replace{have no WAR dependency and are consistent}{in this figure are atomic since they do not have WAR dependency on the variables they are modifying, e.g. \emph{x} is only read and \emph{y} is only written within Task 1.} Now, suppose three tasks have been virtualized into one, namely Task 4: \replace{ \{y=x+1; z=y+1; x=z+1;\} which has inherent WAR dependency (variable \{\tt{x}\}). }{since now \emph{x} is first read and then written, a WAR dependency is introduced dynamically at run-time---unfortunately Task 4 is no more atomic since its re-execution will not always produce the same results.}
